General constraints on magic distillation protocols from statistical mechanics

### 2021-04-21 magic_paper.tex
Removed errors, started discussion on max-thauma, need to include numerical majorisation bounds and perhaps other magic state conversions

Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which is defined via a semi-definite program, but possesses properties that allow for an easy comparison with our bound.
The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
Using the max--thauma properties of super-additivity and vanishing at free states, we obtain
\begin{align}
	&\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon)) \geq (1-\epsilon) \theta_{\rm{max}}(\ketbra{\rm{S}}) + \epsilon \theta_{\rm{max}}\left(\frac{1}{3}\id \right) = \nonumber\\
	&(1-\epsilon) \theta_{\rm{max}}(\rho_{\rm{S}}(0)),
\end{align}
so that for a deterministic single-copy distillation process, an initial number of copies $n \geq \theta_{\rm{max}}(\tau) / \theta_{\rm{max}}(\rho) \geq 1-\epsilon$ is required.
Therefore, the max--thauma bound for the pure Strange state distillation process can get as tight as \nick{CALCULATING THAUMA EXACTLY AT THE MOMENT}
\begin{equation}
	R = \frac{1}{n} = \frac{\theta_{\rm{max}}(\rho_{\rm{S}}(\epsilon))}{\theta_{\rm{max}}(\rho_{\rm{S}}(0))} \leq 1-\epsilon.
\end{equation}

Both the mana and the max--thauma bounds are looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}.

In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective. Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    }
    \label{fig:distill_bounds}
\end{figure}

>>>>

Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which can be defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log_2{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
\end{equation}
and can be calculated numerically via a semi-definite program.

The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
For the noisy Strange state, the max-thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}. 
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    }
    \label{fig:distill_bounds}
\end{figure}

I include in~\cref{fig:test} the purification of Norrell states and the purification of $T$ states.\nick{Need to include numerical majorization curves to compare, extend noise range.}

\begin{figure}[h]
    \centering
    \subfigure[][]{%
    \label{fig:norrell}%
    \includegraphics[height=3cm]{figs/compare_norrell.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:tstate}%
    \includegraphics[height=3cm]{figs/compare_tstate.pdf}}
    \caption{\textbf{Bound comparison} 
    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification;
    }%
    \label{fig:test}
\end{figure}

In the next section we provide relative majorization bounds in arbitrary stabilizer fragments, and in particular we shall parameterize these bounds from a thermodynamic perspective. Specifically, we can interpret the stabilizer state $\sigma$, which defines the fragment, as a thermodynamic equilibrium state at some effective temperature and with some effective Hamiltonian.
